---
title: "Web Scraping in Python"
author: "Hari Patchigolla"
date: "8/1/2022"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Table of Contents


1. Introduction to Web Scraping

    - What is Web Scraping?
    - Data Science Pipeline
    - Where does Web Scraping fit in the Data Science Pipeline?

2. Requests and BeautifulSoup

    - How does Web Scraping work?
    - Static Web Scraping with BeautifulSoup
      - Scraping MLS data

3. Selenium and SQL (sqlite3)

    - How to create web scraping bots
    - Storing scraped data in an SQL database
 
4. Legality of Web Scraping

    - When is it okay to Scrape a website
      - Consequences of scraping a website you are not allowed to scrape
    - Easy ways to know if a website is okay to scrape
      - `/robots.txt`
      - How to read a `robots.txt` file


# Introduction to Web Scraping

## What is Web Scraping?

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

